% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
%Margin setup

\setlength{\voffset}{0.1in}
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{11in}
\setlength{\textheight}{9.5in}
\setlength{\topmargin}{-0.25in}
\setlength{\textwidth}{7in}
\setlength{\topskip}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\evensidemargin}{-0.25in}
%-----------------------------------------------------------
%\usepackage{fullpage}
\usepackage{wasysym}
\usepackage{shading}
%\textheight=9.0in
\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \parashade[.9]{sharpcorners}{\textbf{#1 \vphantom{p\^{E}}}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
\textbf{\Large David Justice} \\
davejustishh-at-gmail.com \\
http://www.davejustice.com \\
\end{tabular*}
\\

\vspace{0.1in}

\resheading{Work Experience}
\begin{itemize}

\item
	\ressubheading{Mozilla}{Remote}{Staff Engineer}{August 2015 - Present}
	\begin{itemize}
		\resitem{Firefox}
    \resitem{Min Vid}
    \resitem{Test Pilot}
	\end{itemize}

\item
	\ressubheading{Rebecca's Bar}{NYC}{Owner/Bartender}{2016 - Present}

\item
	\ressubheading{Freelance Development}{Portland, Oregon}{Software Engineer}{2013 - August 2015}

\item
	\ressubheading{Kerr Tire / Larry's Tire}{Lynchburg, VA}{Automotive Mechanic}{2004 - 2012}
	\begin{itemize}
    \resitem{Front End / Alignment Specialist, general mechanic}
	\end{itemize}

\end{itemize}

\resheading{Open Source Projects}
\begin{itemize}
\item
	\ressubheading{Meta-staseis}{}{http://edit.cassettetap.es}{started 2014}
	\begin{itemize}
		\resitem{Editing Audio Files in a Browser}
    \resitem{Client Side manipulation of audio data in a web worker.}
    \resitem{Supports Copy, Cut, Paste, reverse, merging}
    \resitem{Exporting as a WAV file}
	\end{itemize}

\item
	\ressubheading{NPR Streams}{}{http://npr-streams.com}{started 2014}
	\begin{itemize}
		\resitem{Parsing of 22,000 line xml file of all npr stations.}
    \resitem{Created easy to navigate and fully documented API}
	\end{itemize}

\item
	\ressubheading{4minutesand33seconds}{}{http://4minutesand33seconds.com}{started 2014}
	\begin{itemize}
    \resitem{Recording and real-time audio visualization in browser with WebAudio and WebWorkerAPI.}
		\resitem{Bulk uploads to Amazon s3.}
	\end{itemize}

\item
	\ressubheading{Revisit.link}{}{http://revisit.link}{2014}
	\begin{itemize}
    \resitem{Project for mapping together microservices for image manipulation.}
		\resitem{Collaborated with the creator of chat.meatspac.es and Big Boring System.}
	\end{itemize}

\item
	\ressubheading{Small Modules on NPM}{}{https://www.npmjs.com/\~{}meandave}{2012 - current}
	\begin{itemize}
    \resitem{general utilities}
    \resitem{Command Line utilities}
    \resitem{Canvas API Helpers}
    \resitem{WebAudio API Libraries}
    \resitem{Developer Tools}
	\end{itemize}

\end{itemize}

\resheading{Skills}

\begin{description}
\item[Languages:]
JavaScript, \LaTeX, C/C++, Markdown
\item[Operating Systems:]
Linux, UNIX, MacOSX, Windows
\item[Applications:]
GIMP \& Photoshop, GNU Plot, \LaTeX, InDesign, Emacs, Illustrator, InkScape, Audacity
\item[Miscellaneous:]
strong verbal and written communication skills, excellent troubleshooting and debugging skills, exceptional problem solving skills, good teams skills
\end{description}

\resheading{Interests}

\begin{description}
\item[Computers:] Maintain a plethora of open source packages, mostly on packages published to NPM. Highly proficient in Linux and other UNIX derived systems.
\item[Automotive:] Comfortable fixing basically anything on any vehicle, from eighteen wheelers to mopeds
\item[Musical: \eighthnote] Playing piano \& creating instruments.
\item[Musical continued: \eighthnote] Running a small independent cassette label.
\item[Other:] Harm Reduction, History studies, mathematics, drawing, painting.
\end{description}

\end{document}
