% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
%Margin setup

\setlength{\voffset}{0.1in}
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{11in}
\setlength{\textheight}{9.5in}
\setlength{\topmargin}{-0.25in}
\setlength{\textwidth}{7in}
\setlength{\topskip}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\evensidemargin}{-0.25in}
%-----------------------------------------------------------
%\usepackage{fullpage}
\usepackage{wasysym}
\usepackage{shading}
%\textheight=9.0in
\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \parashade[.9]{sharpcorners}{\textbf{#1 \vphantom{p\^{E}}}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
\textbf{\Large David Justice}  & 434 944 1440\\
1726 SE Division Street & davejustishh-at-gmail.com \\
Portland, OR & http://www.davejustice.com\\
\end{tabular*}
\\

\vspace{0.1in}

\resheading{Work Experience}
\begin{itemize}
\item
	\ressubheading{Freelance Development}{Portland, Oregon}{Software Engineer}{March 2014 - Present}
	\begin{itemize}
		\resitem{Led multiple teams in engineering fresh and legacy projects.}
		\resitem{Implemented an interactive SVG interface representative of complex medical data.}
	\end{itemize}

\item 
	\ressubheading{Quick Left}{Portland, OR}{Software Engineer}{January 2014 - February 2014}
	\begin{itemize}
		\resitem{Assisted in the onboarding of Quick Left engineers in the the Sprint.ly project after the merger.}
	\end{itemize}

\item
	\ressubheading{Sprint.ly}{Portland, OR}{Software Engineer}{January 2013 - January 2014}
	\begin{itemize}
		\resitem{Implemented the popular list view.}
		\resitem{Improved Test Coverage from below 1 percent up to well over 50 percent.}
    \resitem{Managed major refactors of the Front End.}
    \resitem{Made large performance improvements in rendering on the front end.}
	\end{itemize}

\item
	\ressubheading{Glider}{Portland, OR}{Software Engineer}{January 2013 - March 2013}
	\begin{itemize}
		\resitem{Worked on a small team to rapidly build out an alpha release for TechCrunch Disrupt}
    \resitem{Helped to stabilize product.}
		\resitem{Assisted in finding full-time employees to carry on development.}
    \resitem{Implemented interactive signing of documents with canvas API}
    \resitem{Acquired one year later by FPX}
	\end{itemize}

\item
	\ressubheading{Tixie}{Portland, OR}{Front End Developer}{September 2012 - January 2013}
	\begin{itemize}
		\resitem{Implement full site redesign.}
	\end{itemize}

\item
	\ressubheading{Outthink Group}{Lynchburg, VA}{Web Developer}{September 2011 -  2012}
	\begin{itemize}
		\resitem{Implement full site redesign.}
	\end{itemize}

\end{itemize}

\resheading{Open Source Projects}
\begin{itemize}
\item
	\ressubheading{Meta-staseis}{}{http://edit.cassettetap.es}{started 2014}
	\begin{itemize}
		\resitem{Editing Audio Files in a Browser}
    \resitem{Client Side manipulation of audio data in a web worker.}
    \resitem{Supports Copy, Cut, Paste, reverse, merging}
    \resitem{Exporting as a WAV file}
	\end{itemize}

\item
	\ressubheading{NPR Streams}{}{http://npr-streams.com}{started 2014}
	\begin{itemize}
		\resitem{Parsing of 22,000 line xml file of all npr stations.}
    \resitem{Created easy to navigate and fully documented API}
	\end{itemize}

\item
	\ressubheading{4minutesand33seconds}{}{http://4minutesand33seconds.com}{started 2014}
	\begin{itemize}
    \resitem{Recording and real-time audio visualization in browser with WebAudio and WebWorkerAPI.}
		\resitem{Bulk uploads to Amazon s3.}
	\end{itemize}

\item
	\ressubheading{Revisit.link}{}{http://revisit.link}{2014}
	\begin{itemize}
    \resitem{Project for mapping together microservices for image manipulation.}
		\resitem{Collaborated with the creator of chat.meatspac.es and Big Boring System.}
	\end{itemize}

\item
	\ressubheading{Small Modules on NPM}{}{https://www.npmjs.com/\~{}meandave}{2012 - current}
	\begin{itemize}
    \resitem{general utilities}
    \resitem{Command Line utilities}
    \resitem{Canvas API Helpers}
    \resitem{WebAudio API Libraries}
    \resitem{Developer Tools}
	\end{itemize}

\end{itemize}

\resheading{Skills}

\begin{description}
\item[Languages:]
JavaScript, \LaTeX, C/C++, Markdown
\item[Operating Systems:]
Linux, UNIX, MacOSX, Windows
\item[Applications:]
GIMP \& Photoshop, GNU Plot, \LaTeX, InDesign, Emacs, Illustrator, InkScape, Audacity
\item[Miscellaneous:]
strong verbal and written communication skills, excellent troubleshooting and debugging skills, exceptional problem solving skills, good teams skills
\end{description}

\resheading{Interests}

\begin{description}
\item[Computers:] Maintain a plethora of open source packages, mostly on packages published to NPM. Highly proficient in Linux and other UNIX derived systems. Studying Digital Signal Processing.
\item[Musical: \eighthnote] Playing piano \& creating instruments. Running a small independent cassette label.
\item[Musical continued: \eighthnote] Running a small independent cassette label.
\item[Outdoors:] Bicycles, camping, traveling.
\item[Other:] Reading about philosophy, mathematics, music theory, history of computing.
\end{description}

\resheading{Presentations \& Workshops}

\begin{itemize}
\item
	\ressubheading{PDXNode Meetup Group}{Portland, Oregon}{Organizer/Presenter}{2013 - Present}
	\begin{itemize}
		\resitem{Multiple Lightning Talks on small modules}
		\resitem{Presentation on Web Audio API}
	\end{itemize}

\item
	\ressubheading{NodeSchool Workshops}{Portland, Oregon}{Organizer}{2013 - Present}
	\begin{itemize}
		\resitem{Assisted with many of the nodeschool.io workshops}
	\end{itemize}

\item
	\ressubheading{CascadiaJS Conference}{Portland, Oregon}{Organizer}{2014}
	\begin{itemize}
		\resitem{Managing talk recordings, planning, accomodating speakers.}
	\end{itemize}

\item
	\ressubheading{JSConf US}{Amelia Island, Florida}{Volunteer}{2014}
	\begin{itemize}
		\resitem{Helped with ticketing, setup/teardown, accomodating speakers.}
	\end{itemize}
\end{itemize}
  
\end{document}
